Neural networks for solving regression and classification problems

### 2022-11-18 doc/paper.tex

\begin{figure}[H]
\centerline{\includegraphics[width=8in]{figure/fin_heatmap.png}}
\caption{Heatmap for each scheduler, showing the optimal lambda and eta for each method, as well as the best MSE reached (highlighted in red)}
\label{heatmap}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=7in]{figure/fin_sgd_batch_size_all.png}}
\caption{MSE over epochs for different batch sizes, for all different schedulers}
\label{sgdbatch}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=8in]{figure/5000e_adam_v_adagrad.png}}
\caption{MSE test error over 5000 epochs for Adam and Adagrad schedulers}
\label{adam_v_adagrad}
\end{figure}

>>>>

\begin{figure}[H]
\centerline{\includegraphics[width=8in]{figure/fin_heatmap.png}}
\caption{MSE score gridsearch for hyperparameters eta, lambda for different schedulers}
\label{heatmap}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=7in]{figure/SGD_batch_size_100e.png}}
\caption{MSE over epochs for different batch sizes, for all different schedulers}
\label{sgdbatch}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=7in]{figure/5000e_adam_v_adagrad.png}}
\caption{MSE test error over 5000 epochs for Adam and Adagrad schedulers}
\label{adam_v_adagrad}
\end{figure}
